\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2022-01-18 4-5-interactive.Rmd
quick fix after the meeting

```{r interactive-linking, echo = FALSE, out.width="100%", out.height="20%", fig.retina = 2, dpi = 300, fig.cap = "Screenshots of variance of monthly temperature range from 2016 to 2020 in Australia. Crossed linking between the map and the temperature band is implemented in both directions to explore the temperature pattern interactively. The first row is the initial view of the graphic and the latter three show the interactive view after selecting on the map (row 2 and 3) and on the temperature band (row 4).", fig.show='hold'}
knitr::include_graphics(here::here("figures/linking.png"))
knitr::include_graphics(here::here("figures/linking-north.png"))
knitr::include_graphics(here::here("figures/linking-mid.png"))
knitr::include_graphics(here::here("figures/linking-south.png"))
```

@@

Figure \ref{fig:interactive-popup} shows the same content as Figure \ref{fig:interactive-linking} but made with leaflet and popups. A few sites with low temperature variance are selected and these sites still show different patterns: Lady Elloit Island in the Pacific coastline shows a thin temperature band of 5 degree; Birdsville Airport, in the middle of Australia desert, shows a wide temperature range of 10 degree throughout the year; and King Island Airport, in the north-west tip of Tasmania island shows a similar narrow range as Lady Elloits but a maximum and minimum temperature in general. This would suggest variance on itself may not be enough to summarise the temperature variation in Australia and other summary statistics, for example, mean of temperature range or maximum temperature itself, could also be useful to find temperature pattern in Australia.

```{r interactive-popup, echo = FALSE, out.width="45%", out.height="25%", fig.retina = 2, dpi = 300, fig.cap = "Screenshots of variance of monthly temperature range from 2016 to 2020 in Australia. Upon clicking a single station on the leaftlet up, the temperature band will be shown as a subplot in the popup box.", fig.show='hold'}
knitr::include_graphics(here::here("figures/popup.png"))
knitr::include_graphics(here::here("figures/popup-right.png"))
knitr::include_graphics(here::here("figures/popup-mid.png"))
knitr::include_graphics(here::here("figures/popup-south.png"))
```

>>>>

```{r interactive-linking, echo = FALSE, out.width="100%", out.height="20%", fig.retina = 2, dpi = 300, fig.cap = "Exploring temperature variation using linkning of a map and seasonal display. Each row is a screen dump of the process. The top row shows all locations and all temperature profiels. Selecting a location with high variance on the map produces the plot in the second row. The maximum nad minimum temperature is shown using a ribbon.", fig.show='hold'}
knitr::include_graphics(here::here("figures/linking.png"))
knitr::include_graphics(here::here("figures/linking-north.png"))
knitr::include_graphics(here::here("figures/linking-mid.png"))
knitr::include_graphics(here::here("figures/linking-south.png"))
```

@@

Figure \ref{fig:interactive-popup} shows the same content as Figure \ref{fig:interactive-linking} but made with leaflet and popups.

```{r interactive-popup, echo = FALSE, out.width="45%", out.height="25%", fig.retina = 2, dpi = 300, fig.cap = "Screenshots of variance of monthly temperature range from 2016 to 2020 in Australia. Upon clicking a single station on the leaftlet up, the temperature band will be shown as a subplot in the popup box.", fig.show='hold'}
knitr::include_graphics(here::here("figures/popup-mid.png")) 
```

### 2022-01-18 main.tex
quick fix after the meeting

\caption[Screenshots of variance of monthly temperature range from 2016 to 2020 in Australia]{Screenshots of variance of monthly temperature range from 2016 to 2020 in Australia. Crossed linking between the map and the temperature band is implemented in both directions to explore the temperature pattern interactively. The first row is the initial view of the graphic and the latter three show the interactive view after selecting on the map (row 2 and 3) and on the temperature band (row 4).}\label{fig:interactive-linking}
\end{figure}
\end{CodeChunk}

@@

Figure \ref{fig:interactive-popup} shows the same content as Figure
\ref{fig:interactive-linking} but made with leaflet and popups. A few
sites with low temperature variance are selected and these sites still
show different patterns: Lady Elloit Island in the Pacific coastline
shows a thin temperature band of 5 degree; Birdsville Airport, in the
middle of Australia desert, shows a wide temperature range of 10 degree
throughout the year; and King Island Airport, in the north-west tip of
Tasmania island shows a similar narrow range as Lady Elloits but a
maximum and minimum temperature in general. This would suggest variance
on itself may not be enough to summarise the temperature variation in
Australia and other summary statistics, for example, mean of temperature
range or maximum temperature itself, could also be useful to find
temperature pattern in Australia.

@@

{\centering \includegraphics[width=0.45\linewidth,height=0.25\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/popup} \includegraphics[width=0.45\linewidth,height=0.25\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/popup-right} \includegraphics[width=0.45\linewidth,height=0.25\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/popup-mid} \includegraphics[width=0.45\linewidth,height=0.25\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/popup-south}

>>>>

\caption[Exploring temperature variation using linkning of a map and seasonal display]{Exploring temperature variation using linkning of a map and seasonal display. Each row is a screen dump of the process. The top row shows all locations and all temperature profiels. Selecting a location with high variance on the map produces the plot in the second row. The maximum nad minimum temperature is shown using a ribbon.}\label{fig:interactive-linking}
\end{figure}
\end{CodeChunk}

@@

Figure \ref{fig:interactive-popup} shows the same content as Figure
\ref{fig:interactive-linking} but made with leaflet and popups.

@@

{\centering \includegraphics[width=0.45\linewidth,height=0.25\textheight]{/Users/sherryzhang/Documents/research/paper-cubble/figures/popup-mid}
